\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-27 paper/ms.tex
RJObject PGM
Extra thanking

@@

\section*{Acknowledgements}
It is a pleasure to thank Anna Pancoast (Harvard),
Ewan Cameron (Oxford), David Hogg (NYU), and Daniela Huppenkothen (NYU)
for valuable discussions. BJB was supported by a Marsden Fast-Start grant
from the Royal Society of New Zealand.

>>>>

\begin{figure}[ht!]
\begin{center}
\includegraphics[width=0.4\textwidth]{figures/rjobject_pgm.pdf}
\caption{\label{fig:rjobject_pgm}}
\end{center}
\end{figure}

@@

\section*{Acknowledgements}
John Veitch and Jorge Alarcon Ochoa provided helpful comments on an early
version of the manuscript.
It is a pleasure to thank Anna Pancoast (Harvard),
Ewan Cameron (Oxford), David Hogg (NYU), and Daniela Huppenkothen (NYU)
for valuable discussions. BJB was supported by a Marsden Fast-Start grant
from the Royal Society of New Zealand.
